---
title: "hrv2"
author: "Vik Gopal"
date: "14 May 2019"
output: html_document
---

```{r load_libraries, message=FALSE, warning=FALSE}
library(RHRV)
library(tidyverse)
path       = "."
```

## Template plots and analysis

* Read in baseline, exercise and music hrs
* Overlay them (requires zero-ing of time)
    * Display standard errors, outliers, summaries, smooths
* Function to detect return to baseline
* Can we use Poincare plot to detect episodes? Can we use the point at which
correlation drops back to zero?
* Work on storing hr objects in a tibble or data frame.

## Read in files

```{r}
# Load baseline
base_hr <- CreateHRVData()
base_hr <- LoadBeatAscii(base_hr, "baseline.txt", RecordPath=path, scale=0.001)
base_hr <- BuildNIHR(base_hr)
PlotNIHR(base_hr)
#hr = FilterNIHR(hr)

ex_hr <- CreateHRVData()
ex_hr <-  LoadBeatAscii(ex_hr, "after_exercise.txt", RecordPath=path, scale=0.001)
ex_hr <- BuildNIHR(ex_hr)
PlotNIHR(ex_hr)

music_hr <-  CreateHRVData()
music_hr <-  LoadBeatAscii(music_hr, "during_music.txt", RecordPath=path, scale=0.001)
music_hr <-  BuildNIHR(music_hr)
PlotNIHR(music_hr)
```

